Select-based random access to variable-byte encodings

### 2020-03-02 gradu/msc_english_contents.tex
Adds results

\begin{table}
\centering
\caption{Results in milliseconds, smaller is better.\label{table:results1}}
\begin{tabular}{l||c c c c c c} 
 & Bris4v5 & Select4 & Bris8 & Bris8v5 & Select8 \\ 
\hline \hline 
all (5M)        & - & 189.8 & 194.0 & 230.3 & 139.2 \\
all (50M)       & - & 292.0 & 256.0 & 304.4 & 232.7 \\
all (500M)      & - &  -    & 299.9 & 369.2 & 335.1 \\
twolarge (5M)   & - & 164.1 & 93.9  & 216.7 & 117.5 \\
twolarge (50M)  & - & 270.4 & 140.0 & 159.8 & 210.6 \\
twolarge (500M) & - & 381.4 & 169.7 & 383.6 & 307.8 \\

>>>>

\begin{table}
\centering
\caption{Results in milliseconds, smaller is better.\label{table:results1}}
\begin{tabular}{l||c c c c c c} 
& bris8 & bris4 & bris8v5 & bris4v5 & select8 & select4  \\
 \hline \hline 
all (5M)   & 194.10 & 578.20 & 232.30 & 461.80 & 132.00 & 187.60 \\
all (50M)   & 255.40 & 719.10 & 300.70 & 558.90 & 214.20 & 291.00 \\
all (500M)   & 298.10 & 821.90 & 368.10 & 644.90 & 307.20 & 388.10 \\
twolarge (5M)   & 96.40 & 331.70 & 107.70 & 260.20 & 119.40 & 165.20 \\
twolarge (50M)   & 142.30 & 406.50 & 159.30 & 332.10 & 212.10 & 269.20 \\
twolarge (500M)   & 168.50 & 516.10 & 191.80 & 393.80 & 304.90 & 381.30 \\
onelarge (5M)   & 25.80 & 50.80 & 26.90 & 42.30 & 94.60 & 106.10 \\
onelarge (50M)   & 50.00 & 85.30 & 51.00 & 72.30 & 197.90 & 241.00 \\
onelarge (500M)   & 55.10 & 96.80 & 59.10 & 80.50 & 294.30 & 351.70 \\
onlysmall (5M)   & 16.40 & 17.60 & 16.60 & 16.50 & 82.40 & 94.90 \\
onlysmall (50M)   & 31.90 & 36.90 & 32.50 & 31.20 & 186.50 & 226.90 \\
onlysmall (500M)   & 34.60 & 39.40 & 35.10 & 34.10 & 278.00 & 333.90 \\
